---
title: "Car MPG Predictor App"
author: "Anjeanette Sy"
output: 
  html_document:
---

The Car MPG Predictor App is a simple Shiny application that allows users to predict the miles per gallon (MPG) of a car model based on its weight. This document provides a guide on how to use the app effectively.

### Installation

- Make sure you have R and RStudio installed on your machine.
- Open RStudio and install the required packages using the following command:

```{r }
library(shiny)
```

### Running the App
```{r}
shinyApp(ui = source("ui.R")$value, server = source("server.R")$value)
```
### How to Use the App

1. **Select Car Model:**
Choose a car model from the dropdown menu in the app's sidebar. The available options are based on the unique values in the `carb` column of the `mtcars` dataset.

2. **Enter Car Weight:**
Enter the weight of the car in the numeric input field. The weight should be in pounds.

3. **View Predicted MPG:**
After selecting a car model and entering the weight, the app will display the predicted MPG for the chosen car model based on the entered weight.


